---
title: Extract your publication list from google scholar in R
author: ''
date: '2022-09-02'
slug: extract-your-publication-list-from-google-scholar-in-r
output:
  blogdown::html_page:
    toc: true
categories:
  - R
  - academic
tags:
  - scholar
---

I have been spending hours to list my pubs for my CV or co-authors for a grant proposal. But now, we can automate this process with R package `scholar` (see [R documentation](https://www.rdocumentation.org/packages/scholar/versions/0.2.4) for general guidance). With some `stringr` and `dplyr` functions, it's pretty easy to export a table of pubs/coauthors via Rmarkdown (if you are unfamiliar with Rmarkdown, see [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/)). A procedure would be:

1.  extract your pub list
2.  transform with `stringr` & `dplyr` functions
3.  export with Rmarkdown (or simply `write_csv()`)

## Publication list

A quick example for a pub list:

```{r}

## GET YOUR PUB LIST

# library -----------------------------------------------------------------

rm(list = ls())
pacman::p_load(tidyverse,
               scholar)

# data --------------------------------------------------------------------

## your google id - can be found in a link bar of your google scholar page
sid <- "H9OuCKsAAAAJ"

## get publication list
pubs <- get_publications(sid) %>% 
  as_tibble()

## html output - needs adjusments for word/pdf outputs
pubs %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_paper() %>% 
  kableExtra::scroll_box(height = "300px")
```

## Coauthor list

Quick example for a co-author list:

```{r}

## get coauthor list
coauthor <- pubs %>% 
  rowwise() %>%
  summarise(year = year,
            authors = get_complete_authors(sid,
                                           pubid,
                                           initials = FALSE))
## one author per row
df_coauthor <- coauthor %>% 
  rowwise() %>% 
  summarize(year = year,
            author = str_split(authors,
                               pattern = ",\\s") %>% 
              flatten_chr()) %>% 
  filter(year >= 2019,
         author != "Akira Terui") %>% 
  distinct(author) %>% 
  separate(author,
           into = c("a", "b", "last"),
           sep = "\\s",
           fill = "left") %>% 
  mutate(first = ifelse(is.na(a), b, paste(a, b)),
         full = paste(last, first, sep = ", ")) %>% 
  select(-a, -b) %>% 
  arrange(last)

## html output - needs adjusments for word/pdf outputs
df_coauthor %>% 
  kableExtra::kbl() %>% 
  kableExtra::kable_paper() %>% 
  kableExtra::scroll_box(height = "300px")
```

Outputs can be saved as `.pdf`, `.html`, or `.docx` via Rmarkdown.
